\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-08 poster/main.tex
update poster

Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$

Bernoulli likelihood function:
  $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$
where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;

Posterior distribution derived: 
$\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$

@@

Our approach defines the mechanism $\hexpmech$: given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, produces an element $r$ in $\betaset$ with probability:
$\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.$

The smooth sensitivity is
computed as follows:
\begin{equation*}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
\end{equation*}
where $d$ is the Hamming distance between two datasets,
$\gamma =
\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $\Delta_{l}\bigg
(\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism. That is:
\begin{equation*}
\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
\end{equation*}

>>>>

Observed data set $\dataobs$: $\dataobs= (x_1,\dots x_n), x_i\in\{0,1\}$, $n\in\mathbb{N}$;

Bernoulli likelihood function: $\Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;

Posterior distribution derived: 
$\Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.

@@

Our approach defines the mechanism $\hexpmech$:

Producing an element $r$ in $\betaset$ with:
$
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
\frac 
{exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\displaystyle\sum_{r\in\betaset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
$,
(given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$).

$\betaset$ is the candidates set defined as $ \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.

The scoring function is instantiated by Hellinegr distance between two beta distributions, and $S(\dataobs)$ is the smooth sensitivity computed as:
$
S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\}
$,
where $d$: Hamming distance between two datasets,

$LS(\dataobs')$ denotes the local sensitivity at $\bysinfer(\dataobs')$:
$
LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
$ and 
$\gamma =
\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure the $(\epsilon,\delta)$-differentially private.
